### 2019-03-27 _publications/jors/paper.tex
Changes requested by Peter

@@

See the contributors list on GitHub~\cite{contributors}.

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology. S.J.D
wishes to acknowledge funding from the U.S. Department of Energy,
Office of Basic Energy Sciences, Division of Materials Sciences and
Engineering under Award \#DE-SC0008637 as part of the Center for
PRedictive Integrated Structural Materials Science (PRISMS Center) at
University of Michigan.

>>>>

This list is for contributors to the code base, but not those that
have only uploaded output results to the website.

@@

Also, see the contributors list on GitHub~\cite{contributors}.

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology. S.J.D
wishes to acknowledge funding from the U.S. Department of Energy,
Office of Basic Energy Sciences, Division of Materials Sciences and
Engineering under Award \#DE-SC0008637 as part of the Center for
PRedictive Integrated Structural Materials Science (PRISMS Center) at
University of Michigan. PWV is grateful for the financial assistance
under the award 70NANB14H012 from the National Institute of Standards
and Technology as part of the Center for Hierarchical Materials Design
(CHiMaD).
